Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-08 talk/dls2012/paper.tex
comment
The number of lines has grown

\newboolean{showcomments}
\setboolean{showcomments}{false}
\ifthenelse{\boolean{showcomments}}
  {\newcommand{\nb}[2]{
    \fbox{\bfseries\sffamily\scriptsize#1}
    {\sf\small$\blacktriangleright$\textit{#2}$\blacktriangleleft$}
   }
   \newcommand{\version}{\emph{\scriptsize$-$Id: main.tex 19055 2008-06-05 11:20:31Z cfbolz $-$}}
  }
  {\newcommand{\nb}[2]{}
   \newcommand{\version}{}
  }

\newcommand\cfbolz[1]{\nb{CFB}{#1}}
\newcommand\arigo[1]{\nb{AR}{#1}}
\newcommand\fijal[1]{\nb{FIJAL}{#1}}
\newcommand\david[1]{\nb{DAVID}{#1}}
\newcommand\anto[1]{\nb{ANTO}{#1}}
\newcommand\reva[1]{\nb{Reviewer 1}{#1}}
\newcommand\revb[1]{\nb{Reviewer 2}{#1}}
\newcommand\revc[1]{\nb{Reviewer 3}{#1}}
\newcommand\revd[1]{\nb{Reviewer 4}{#1}}
\newcommand{\commentout}[1]{}
\newcommand{\ignore}[1]{} % {{\tt \small ignore(#1)}}

@@

  arrays. It is implemented as a two nested loops that iterates over the elements of the 

@@

  using sobel derivatives. A Sobel x-derivative $D_x$ of a $n \times n$ image ${I}$ is formed

@@

    -2 & 0 & 1 \\

@@

and a Sobel y-derivative $D_y$ is formed convolving with $K^\top$. The gradient magnitude is 

@@

\revc{
The discussion of LuaJIT is unsatisfying.  It's not clear to me from that one
quote that Mike is doing the same thing.  It might be worth including LuaJIT in
the benchmarks, and/or examining the actual implementation of LuaJIT.
}
\cfbolz{maybe we can look in the new LuaJIT wiki.
how annoying would it be to rerun the benchmarks, if I can find somebody to write them?}

>>>>

\newboolean{showcomments}
\setboolean{showcomments}{true}
\ifthenelse{\boolean{showcomments}}
  {\newcommand{\nb}[2]{
    \fbox{\bfseries\sffamily\scriptsize#1}
    {\sf\small$\blacktriangleright$\textit{#2}$\blacktriangleleft$}
   }
   \newcommand{\version}{\emph{\scriptsize$-$Id: main.tex 19055 2008-06-05 11:20:31Z cfbolz $-$}}
  }
  {\newcommand{\nb}[2]{}
   \newcommand{\version}{}
  }

\newcommand\cfbolz[1]{\nb{CFB}{#1}}
\newcommand\arigo[1]{\nb{AR}{#1}}
\newcommand\fijal[1]{\nb{FIJAL}{#1}}
\newcommand\david[1]{\nb{DAVID}{#1}}
\newcommand\anto[1]{\nb{ANTO}{#1}}
\newcommand\hakan[1]{\nb{HAKAN}{#1}}
\newcommand\reva[1]{\nb{Reviewer 1}{#1}}
\newcommand\revb[1]{\nb{Reviewer 2}{#1}}
\newcommand\revc[1]{\nb{Reviewer 3}{#1}}
\newcommand\revd[1]{\nb{Reviewer 4}{#1}}
\newcommand{\commentout}[1]{}
\newcommand{\ignore}[1]{} % {{\tt \small ignore(#1)}}

@@

  arrays. It is implemented as two nested loops that iterates over the elements of the 

@@

  using sobel derivatives. A Sobel x-derivative, $D_x$, of a $n \times n$ image, ${I}$, is formed

@@

    -2 & 0 & 2 \\

@@

and a Sobel y-derivative, $D_y$, is formed convolving $I$ with $K^\top$. The gradient magnitude is 

@@

\revc{
The discussion of LuaJIT is unsatisfying.  It's not clear to me from that one
quote that Mike is doing the same thing.  It might be worth including LuaJIT in
the benchmarks, and/or examining the actual implementation of LuaJIT.
}
\cfbolz{maybe we can look in the new LuaJIT wiki.
how annoying would it be to rerun the benchmarks, if I can find somebody to write them?}
\hakan{there is iwtc11/benchmarks/runall.sh which is supposed to run them all}
